---
title: "Untitled"
author: "Rachel Slimovitch"
date: "2023-10-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(here)
library(tidyverse)
library(knitr) # to format tables
library(lubridate) # to help extract the date
library(covidcast)
library(survey)
library(tableone) # tableone
library(kableExtra)
library(magrittr)
library(data.table)
library(readxl)
library(glmtoolbox)
library(MASS)  #for logistic reg
library(RColorBrewer)

here::i_am("code/10_7.rmd")
```



#############################################################################
ASSOCIATION
- Run code from 10_7.Rmd to get data

Time point #1: Dec 1-23 (before closing for holidays)
Time point #2: May 2021 (May 1-May 20, before schools in the south close for summer)

svyglm: survey-weighted generalized linear models

#############################################################################

Start w/anxiety: December data
```{r}

#since 82% have "none" or "some" anxiety and 18% have "most" or "all of the time" --> dichotomize
d4a_noNA_anx<- d4a %>%
  mutate(anxiety=as.integer(anxiety)) %>%
  filter(!is.na(anxiety)) %>%
  mutate(
    anxiety_binary= ifelse (anxiety %in% c(1,2), 0, 1),
    anxiety_binary=as.integer(anxiety_binary),
    gender=dplyr::recode(gender, "1"="Male", "2"="Female", "3"="Non-binary", "4"="Prefer to self-describe", "5"="Prefer not to answer"))

#Dec
d4a_anx_dec<- d4a_noNA_anx %>%
  filter(date >= "2020-12-01") %>%
  filter(date<= "2020-12-23") %>%
  mutate(age=as.numeric(age))

```

QUICK CHECK:
- age as continuous?
```{r}
#Calculate mean of anxiety_binary in each group- does it look linear? - generally yes (ignore NA age)
#looked even more continuous w/December
age_proportions <- d4a_noNA_anx %>%
  group_by(age) %>%
  summarise(success_rate = weighted.mean(anxiety_binary), w = weight) 

ggplot(age_proportions, aes(x = age, y = success_rate)) +
  geom_point() +
  xlab("Binned Age") +
  ylab("Proportion of Successes") +
  ggtitle("Scatter Plot of Binned Age vs. Proportion of Successes")

```

#############################################################################
Model 1
- only predictors are in-person and hybrid
#############################################################################

December:
```{r}
anxiety_design_dec<- svydesign(ids = ~1, weights = ~weight, data = d4a_anx_dec) 
mod_anxiety1_dec <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0, design=anxiety_design_dec, family=binomial)

##########QUESTION: why am I getting warning: "Warning: non-integer #successes in a binomial glm?"
count(x = d4a_anx_dec, anxiety_binary) %>% mutate(proportion = percent(n / sum(n))) #only 0 or 1 outcome
#and I don't get that error when I ignore the survey weights:
try_noweight_dec_anxiety <- glm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0, data=d4a_anx_dec, family=binomial)
summary(try_noweight_dec_anxiety) #get similar output as w/weights


summary(mod_anxiety1_dec)

#May
d4a_anx_may<-d4a_noNA_anx %>%
  filter(date >= "2021-05-01") %>%
  filter(date<= "2021-05-20") %>%
  mutate(age=as.numeric(age))
  
anxiety_design_may<- svydesign(ids = ~1, weights = ~weight, data = d4a_anx_may) 
mod_anxiety1_may <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0, design=anxiety_design_may, family=binomial)
summary(mod_anxiety1_may)


```

#############################################################################
Model 2
- consider age and gender as well
#############################################################################

```{r}
#Dec

mod_anxiety2_dec <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender, design=anxiety_design_dec, family=binomial)

summary(mod_anxiety2_dec)


#May
mod_anxiety2_may <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender, design=anxiety_design_may, family=binomial)

summary(mod_anxiety2_may)

```

#############################################################################
Model 3
- age, gender, region
#############################################################################

```{r}
#Dec
mod_anxiety3_dec <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender + REGION, design=anxiety_design_dec, family=binomial)

summary(mod_anxiety3_dec)


#May
mod_anxiety3_may <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender + REGION, design=anxiety_design_may, family=binomial)

summary(mod_anxiety3_may)

```


#############################################################################
Model 4
- age, gender, region, pct_dem, comorbidities
#############################################################################

```{r}
#Dec
mod_anxiety4_dec <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender + REGION + pct_dem + comorbid, design=anxiety_design_dec, family=binomial)

summary(mod_anxiety4_dec)


#May
mod_anxiety4_may <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0 +
                             age + gender + REGION + pct_dem + comorbid, design=anxiety_design_may, family=binomial)

summary(mod_anxiety4_may)

```

#############################################################################
Other thought: use logistic regression so output is restricted to between 0 and 1
- but outcome of anxiety is not rare: so can't estimate RR. OR really weird to interpret
- could use modified Poisson model?
#############################################################################

```{r}
mod_anxiety1_dec_logistic <- svyglm(anxiety_binary ~ modality_in_person_1_0 + modality_part_time_1_0, design=anxiety_design_dec, family=binomial(link="logit"))
summary(mod_anxiety1_dec_logistic)
#OR in person = exp(-0.066) = 0.94. The odds of having medium or high anxiety is 0.94 times the odds of having low or no anxiety compared to those have a kid in person vs those who have a kid remote.
```

#############################################################################
Other thought: as I control for covariates, do I restrict data so I have complete cases for those covariates?
#############################################################################

```{r}
#example: model 2, december. Age and gender
#Dec
d4a_anx_dec_mod2<- d4a_anx_dec %>%
    filter(!is.na(age)) %>%
    filter(!is.na(gender))  #212046 obs
```
