---
title: "10/7"
author: "Rachel Slimovitch"
date: "2023-10-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(here)
library(tidyverse)
library(knitr) # to format tables
library(lubridate) # to help extract the date
library(covidcast)
library(survey)
library(tableone) # tableone
library(kableExtra)
library(magrittr)
library(data.table)
library(readxl)
library(glmtoolbox)
library(MASS)  #for logistic reg
library(RColorBrewer)

here::i_am("code/10_7.rmd")
```

#############################################################################
READ IN DATA CORRECTLY:
#############################################################################

```{r}
# set up data table
d = data.table()

#files: nov2020 to may2021
files=c("2020-11.csv","2020-12.csv","2021-01.csv","2021-02.csv","2021-03.csv","2021-04.csv","2021-05.csv")

# read in and bind data files
for(i in 1:length(files)){
  temp = fread(here("Data", files[i]))
  d = rbindlist(list(d, temp), fill = TRUE)
  print(i)
}

# link zip code to state- CHANGE TO MATCH ALYSSA'S CODE
zip = data.table(read_excel(here("Data", "ZIP_Alyssa.xlsx"))) %>%
  dplyr::select(ZIP, USPS_ZIP_PREF_STATE) %>% unique()

#merge to data
d<- d %>% 
  left_join(zip %>% 
           dplyr::select(ZIP, USPS_ZIP_PREF_STATE), #we only want these vars
           by = c("A3" = "ZIP"))

#add on region: using state_census data
d1<-d %>%
  left_join(state_census %>%
              dplyr::select(REGION, ABBR),
              by = c("USPS_ZIP_PREF_STATE" = "ABBR"))

#CHECK PROPORTIONS
#unweighted
proportions <- count(x = d1, REGION) %>%
  mutate(proportion = percent(n / sum(n)))

#weighted
proportions <- count(x = d1, REGION, wt = weight) %>%
  mutate(proportion = percent(n / sum(n)))

```

#############################################################################
DATA CLEANING
*Note:* If included till Nov2021, exclude 2021-09-04 (errors)
- date as date format, rename as "date" DONE
- one variable for anxiety DONE
- one variable for depression DONE
- one variable for isolation  DONE
- rename age, gender, grades, modality DONE
- create remote variable DONE
- make modality 1 or 0

#############################################################################

```{r}
#date
d1 <- d1 %>%
  mutate(
    StartDatetime = ymd_hms(StartDatetime), #StartDateTime as DateTime object
    date = as.Date(StartDatetime) #create new variable date
  )


#STEP 2: 
#create one variable for anxiety for Waves 5-11
#rename age, gender, modality of schooling
#create variable for remote (at least 1 child is learning fully remote)
d2 <- d1 %>%
    mutate(A5_1 = as.numeric(A5_1)) %>%
    filter(!is.na(A5_1) & A5_1 >= 1 & A5_1<=20) %>% #at least 1 kid
    rename(
    age = D2,
    gender = D1,
    prek_or_k = E1_1,
    grades1_5 = E1_2,
    grades6_8 = E1_3,
    grades9_12 = E1_4,
    modality_in_person = E2_1,
    modality_part_time = E2_2,
    hh_num_children=A5_1
  ) 

d2<-d2 %>%
  mutate(
    anxiety = ifelse(!is.na(C8_1), C8_1, ifelse(!is.na(C8a_1), C8a_1, C18a)),
    depression = ifelse(!is.na(C8_2), C8_2, ifelse(!is.na(C8a_2), C8a_2, C18b)),
    isolation = ifelse(!is.na(C8_3), C8_3, C8a_3),
    modality_remote = ifelse((prek_or_k > 0 | grades1_5 > 0 | grades6_8 > 0 | grades9_12 > 0) &
                             modality_in_person == 3 & modality_part_time == 3, 1, 0),
    modality_part_time_1_0 = ifelse(modality_part_time == 2, 1,
                                     ifelse(modality_part_time == 3, 0, "NA")),
    modality_in_person_1_0 = ifelse(modality_in_person == 2, 1,
                                     ifelse(modality_in_person == 3, 0, "NA")),
    comorbid = case_when(
      C1 == "9" ~ "0", !grepl(",", C1) & C1 != "9" ~ "1", grepl(",", C1) & !grepl("9", C1) & length(unlist(strsplit(C1, ","))) >= 2 ~ "2+")
  ) 

#continue filtering parent: must have 1 kid in school (prek to grade 12)
d3<- d2 %>%
  filter(prek_or_k>=1 | grades1_5>=1 | grades6_8>=1 | grades9_12>=1) 

d4<-d3 %>%
  filter(!is.na(modality_in_person_1_0) & !is.na(modality_part_time_1_0))  %>% #both are left unanswered
  filter(modality_in_person_1_0 !="NA" & modality_part_time_1_0 !="NA") #both are recorded as "don't know"


```

#############################################################################
Create Table 1:
- stratified by modality
- not stratified
#############################################################################

```{r}
#make variables factor: age, region, gender, comorbid
d4<- d4 %>%
  mutate(
    REGION = as.factor(REGION),
    REGION=dplyr::recode(REGION, "1"="Northeast", "2"="Midwest", "3"="South", "4"="West"),
    age = as.factor(age),
    gender = as.factor(gender),
    comorbid = as.factor(comorbid),
    #prek or k
    prek_or_k=as.factor(prek_or_k),
    prek_or_k = dplyr::recode(prek_or_k, "2" = "0"),
    prek_or_k = fct_relevel(prek_or_k, "0", "1"),
    #grades1-5
    grades1_5=as.factor(grades1_5),
    grades1_5 = dplyr::recode(grades1_5, "2" = "0"),
    grades1_5 = fct_relevel(grades1_5, "0", "1"),
    #grades6-8
    grades6_8=as.factor(grades6_8),
    grades6_8 = dplyr::recode(grades6_8, "2" = "0"),
    grades6_8 = fct_relevel(grades6_8, "0", "1"),
    #grades9-12
    grades9_12=as.factor(grades9_12),
    grades9_12 = dplyr::recode(grades9_12, "2" = "0"),
    grades9_12= fct_relevel(grades9_12, "0", "1"),
  )




```


#############################################################################
Merge data with voting:
#############################################################################

```{r}
#ran in ArcGIS: JSON to features (from NY Times data)
votes_zip<-read.csv("/Users/rachelslimovitch/Documents/23-24/Brown/Thesis/Data/Votes_Zip.csv")

#get FIPS
votes_zip2<-votes_zip %>%
  #make numeric, exclude where no votes
  mutate(
    DEM=as.numeric(DEM),
    TOTAL=as.numeric(TOTAL)) %>%
  filter(!TOTAL==0) %>%
  #get first 5 digts from ID: FIPS code
  mutate(fips = substr(ID, 1, 5))

#sort by FIPS: combine votes, % dem by FIPS
votes_zip3 <- votes_zip2 %>%
  mutate(fips = as.numeric(fips)) %>%
  group_by(fips) %>%
  summarize(
    TotalVotes = sum(TOTAL),
    TotalDEM = sum(DEM)
  ) %>%
  mutate(pct_dem = TotalDEM / TotalVotes)

d4a<- merge(d4, votes_zip3, by="fips")

#add column: with quartiles
quartiles <- quantile(d4a$pct_dem, probs = c(0.25, 0.5, 0.75))

d4a<- d4a %>%
  mutate(
    quartile = ifelse(pct_dem < quartiles[1], "quartile 1",
                      ifelse(pct_dem < quartiles[2], "quartile 2",
                             ifelse(pct_dem < quartiles[3], "quartile 3", "quartile 4")))
  )
```


Table:
```{r}

#make long dataframe: column for modality
d5<- d4%>%
  mutate(modality_remote = as.character(modality_remote)) %>%
  pivot_longer(cols = c("modality_in_person_1_0", "modality_remote", "modality_part_time_1_0"), 
               names_to = "modality", #column that contains type of modality
               values_to = "modality_value") %>% #column that contains what the value is
  filter(modality_value == 1)

#vars
vars_tbl<- c('age', 
            'hh_num_children',
            'REGION', 
            'gender',
            'comorbid',
            'prek_or_k', 
            'grades1_5', 
            'grades6_8', 
            'grades9_12')

survey_design_d5<-svydesign(id=~1,
          data=d5, 
          weights=d5$weight)

table_d5 <- svyCreateTableOne(
      vars = c(vars_tbl),  # List the variables you want to include
      data = survey_design_d5,
      strata="modality"
)

kableone(table_d5) %>%
      add_header_above(c("Table 1: Summary of Distributions of Covariates, Stratified by Modality (Weighted) "=6))%>%
      kable_styling(position="center") %>%
      kable_styling(latex_options= c("HOLD_position")) 

table_d5_overall <- svyCreateTableOne(
      vars = c(vars_tbl),  # List the variables you want to include
      data = survey_design_d5
)

kableone(table_d5_overall) %>%
      add_header_above(c("Table 1: Summary of Distributions of Covariates (Weighted) "=6))%>%
      kable_styling(position="center") %>%
      kable_styling(latex_options= c("HOLD_position")) 
```


#############################################################################
Plots:
- region
- dem vote
- comorbidities
- covid concern

Then, 2x2 facets:
- region * dem vote
- region * comorbidities
- region * covid concern
#############################################################################

*First:* Overall
```{r}
days_per_group<- 7

d4a_summarized <- d4a %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#anxiety: each pt is week avg for that modality
ggplot(d4a_summarized %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point() +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality") 

#depression
ggplot(d4a_summarized %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point() +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, overall") 

#isolation (ends May 20)
ggplot(d4a_summarized %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point() +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Isolation",
       title = "Scatterplot of Average Isolation by Modality, overall") 

```

Region: 
```{r}
d4a_region <- d4a %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, REGION) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#anxiety: each pt is week avg for that modality
ggplot(d4a_region %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Region") +
       facet_wrap(~REGION) 

#depression
ggplot(d4a_region %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, Stratified by Region") +
       facet_wrap(~REGION) 

#isolation (ends May 20)
ggplot(d4a_region %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Isolation",
       title = "Scatterplot of Average Isolation by Modality, Stratified by Region") +
       facet_wrap(~REGION) 
```
Pct democrat vote:
```{r}
d4a_pct_dem <- d4a %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, quartile) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#anxiety: each pt is week avg for that modality
ggplot(d4a_pct_dem %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Quartile of Democratic Vote") +
       facet_wrap(~quartile) 

#depression
ggplot(d4a_pct_dem %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality,Stratified by Quartile of Democratic Vote") +
       facet_wrap(~quartile) 

#isolation (ends May 20)
ggplot(d4a_pct_dem %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Isolation",
       title = "Scatterplot of Average Isolation by Modality,Stratified by Quartile of Democratic Vote") +
       facet_wrap(~quartile) 
```
Comorbidities:
```{r}
d4a_comorbid <- d4a %>%
  filter(!is.na(comorbid)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, comorbid) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#anxiety: each pt is week avg for that modality
ggplot(d4a_comorbid%>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Comorbidities") +
       facet_wrap(~comorbid) 

#depression
ggplot(d4a_comorbid %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality,Stratified by Comorbidities") +
       facet_wrap(~comorbid) 

#isolation (ends May 20)
ggplot(d4a_comorbid %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Isolation",
       title = "Scatterplot of Average Isolation by Modality,Stratified by Comorbidities") +
       facet_wrap(~comorbid) 
```
Covid concern:
```{r}
d4a_concern <- d4a %>%
  mutate(C9=dplyr::recode(C9, "1"="Very worried", "2"="Somewhat worried", "3"="Not too worried", "4"="Not worried at all")) %>%
  filter(!is.na(C9)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, C9) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#anxiety: each pt is week avg for that modality
ggplot(d4a_concern %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Covid Concern") +
       facet_wrap(~C9) 

#only less worried:
concern_low <- d4a_concern %>%
  filter(C9 %in% c("Not too worried", "Not worried at all")) 

ggplot(concern_low %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Covid Concern") +
       facet_wrap(~C9) 

#only more worried:
concern_high <- d4a_concern %>%
  filter(C9 %in% c("Very worried", "Somewhat worried")) 

ggplot(concern_high %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, Stratified by Covid Concern") +
       facet_wrap(~C9) 

#depression
ggplot(d4a_concern %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality,Stratified by Covid Concern") +
       facet_wrap(~C9) 

#isolation (ends May 20)
ggplot(d4a_concern %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), aes(x = date_group, y = value, group = var, color=var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se=F) +
  labs(x = "Date", 
       y = "Average Isolation",
       title = "Scatterplot of Average Isolation by Modality,Stratified by Covid Concern") +
       facet_wrap(~C9) 
```
#############################################################################
2x2 facets:
- region * dem vote
- region * comorbidities
- region * covid concern
#############################################################################

Region + dem vote:
```{r}
d4a_region_dem <- d4a %>%
  mutate(date=as.Date(date)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, quartile, REGION) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#Anxiety
ggplot(d4a_region_dem %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, by dem vote and region") +
  facet_grid(quartile ~REGION)

#Depression
ggplot(d4a_region_dem %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, by dem vote and region") +
  facet_grid(quartile ~REGION)

#Isolation
ggplot(d4a_region_dem %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average isolation",
       title = "Scatterplot of Average Isolation by Modality, by dem vote and region") +
  facet_grid(quartile ~REGION)

```

Region + comorbidities:
```{r}
d4a_region_comorbid <- d4a %>%
  mutate(date=as.Date(date)) %>%
  filter(!is.na(comorbid)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, comorbid, REGION) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#Anxiety
ggplot(d4a_region_comorbid %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, by comorbidities and region") +
  facet_grid(REGION ~comorbid)

#only 0 or 1 comorbidity:
comorbid_0_1<- d4a_region_comorbid %>%
  filter(comorbid %in% c("0", "1")) 

ggplot(comorbid_0_1 %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, by comorbidities and region") +
  facet_grid(REGION ~comorbid)

#Depression
ggplot(d4a_region_comorbid %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, by comorbidities and region") +
  facet_grid(REGION ~comorbid)

#Isolation
ggplot(d4a_region_comorbid %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average isolation",
       title = "Scatterplot of Average Isolation by Modality, by comorbidities and region") +
  facet_grid(REGION ~ comorbid)

```

Region + covid concern:
```{r}
d4a_region_concern <- d4a %>%
  mutate(date=as.Date(date)) %>%
  mutate(C9=dplyr::recode(C9, "1"="1)Very worried", "2"="2)Somewhat worried", "3"="3)Not too worried", "4"="4)Not worried at all")) %>%
  filter(!is.na(C9)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, C9, REGION) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#Anxiety
ggplot(d4a_region_concern %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.5) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, by concern and region") +
  facet_grid(REGION ~C9) +
  scale_color_brewer(palette="Dark2")

#Depression
ggplot(d4a_region_concern %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, by concern and region") +
  facet_grid(REGION ~C9)

#Isolation
ggplot(d4a_region_concern %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average isolation",
       title = "Scatterplot of Average Isolation by Modality, by concern and region") +
  facet_grid(REGION ~ C9)

```
Dem vote *comorb:
```{r}
d4a_dem_comorbid <- d4a %>%
  mutate(date=as.Date(date)) %>%
  filter(!is.na(comorbid)) %>%
  mutate(date_group = cut(date, breaks = seq(min(date), max(date) + 1, by = paste(days_per_group, "days")), labels = FALSE)) %>%
  group_by(date_group, comorbid, quartile) %>%
  #anxiety, depression, isolation
  summarize(
    #anxiety
        avg_anxiety_remote = weighted.mean(ifelse(modality_remote == 1, anxiety, NA), na.rm = TRUE, w = weight), 
        avg_anxiety_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
        avg_anxiety_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, anxiety, NA), na.rm=TRUE, w=weight),
    #depression
        avg_depression_remote = weighted.mean(ifelse(modality_remote == 1, depression, NA), na.rm = TRUE, w = weight), 
        avg_depression_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, depression, NA), na.rm=TRUE, w=weight),
        avg_depression_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, depression, NA), na.rm=TRUE, w=weight),
    #isolation
        avg_isolation_remote = weighted.mean(ifelse(modality_remote == 1, isolation, NA), na.rm = TRUE, w = weight), 
        avg_isolation_hybrid = weighted.mean(ifelse(modality_part_time_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
        avg_isolation_inperson = weighted.mean(ifelse(modality_in_person_1_0==1, isolation, NA), na.rm=TRUE, w=weight),
    num_observations = n()
  )

#Anxiety
ggplot(d4a_dem_comorbid %>% 
  gather(var, value, avg_anxiety_remote, avg_anxiety_hybrid, avg_anxiety_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.4) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Anxiety",
       title = "Scatterplot of Average Anxiety by Modality, by # of Comorbidities and % Democratic Vote") +
  facet_grid(quartile ~comorbid) +
  scale_color_brewer(palette="Dark2") +
  theme(plot.title = element_text(size = 10))

#Depression
ggplot(d4a_dem_comorbid %>% 
  gather(var, value, avg_depression_remote, avg_depression_hybrid, avg_depression_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average Depression",
       title = "Scatterplot of Average Depression by Modality, by # of Comorbidities and % Democratic Vote") +
  facet_grid(quartile ~comorbid) +
  scale_color_brewer(palette="Dark2") +
  theme(plot.title = element_text(size = 10))

#Isolation
ggplot(d4a_dem_comorbid %>% 
  gather(var, value, avg_isolation_remote, avg_isolation_hybrid, avg_isolation_inperson), 
  aes(x = date_group, y = value, group = var, color = var)) +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(se = FALSE) +
  labs(x = "Date", 
       y = "Average isolation",
       title = "Scatterplot of Average Isolation by Modality, by # of Comorbidities and % Democratic Vote") +
  facet_grid(quartile~ comorbid) +
  scale_color_brewer(palette="Dark2") +
  theme(plot.title = element_text(size = 10))



```



